### 2022-07-17 paper/akweury/document.tex
upload an2 model

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

@@

\subsection{Light Map}
The light map $ L $ can be derived from vertex map and the light source position. As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
\begin{equation}\label{light-direction}
	\begin{array}{ll}
		L(x,y)&= \frac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
	\end{array}
\end{equation}
where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space. The light direction map $ L $ is normalized since only the direction of the light is considered. 
The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.

@@

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
\end{tikzpicture}

\caption{Light Net for light inpainting based on GCNN architecture.}
\label{fig:light-net-archi}
\end{figure}

\subsection{Light and image guided normal inference using GCNN}
Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference. The structure is shown in Figure \ref{fig:albedo-gated-archi}. As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.

>>>>

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}
\subimport{./layers/}{init}
\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\DcnvColor{rgb:blue,5;green,2.5;white,5}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\SumColor{rgb:blue,5;green,15}
\def\poolsep{1}

@@

\subsection{Light Map}
\label{sec:lightmap}
The light map $ L $ can be derived from vertex map and the light source position. As shown in Figure \ref{fig:lambertian-surface}, the incoming light direction is a vector point from light source to the surface point, therefor it can be calculated as follows
\begin{equation}\label{light-direction}
	\begin{array}{ll}
		L(x,y)&= \frac{V(x,y)-(s_x,s_y)}{\|V(x,y)-(s_x,s_y)\|_2}\\ 
	\end{array}
\end{equation}
where $ (s_x,s_y) $ is the light source position and $ V $ is the vertices, both $  (s_x,s_y) $ and  $ V $ are with respect to the camera space. The light direction map $ L $ is normalized since only the direction of the light is considered. 
The light map is a matrix corresponding the light direction of whole image where each pixel corresponding with each other, thus it has the same size as the vertex map.

@@

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
\end{tikzpicture}
\caption{Light Net for light inpainting based on GCNN architecture.}
\label{fig:light-net-archi}
\end{figure}

\subsection{Light and image guided normal inference using GCNN}
Based on above implementations, we propose a Three branches Gated Convolutional Neural Network (TriGNet) to perform guided normal inference. The structure is shown in Figure \ref{fig:albedo-gated-archi}. As mentioned in the name, the network utilizes the GCNN architecture three times to accomplish the task. The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings. 
The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
The third branch takes the 3D vertex map as the input. The structure is based on GCNN architecture. However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part. Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling. Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32. After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.

\begin{sidewaysfigure}[th]
	\centering
	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
	\caption{The architecture of TriGNet}
	\label{fig:albedo-gated-archi}
\end{sidewaysfigure}
